\Large{All in the family:\\German twin finishing times in\\the 2016 women's Olympic marathon}

### 2017-02-03 paper/paper.tex
correct figure

\title{\Large{All in the family:\\Anna and Lisa Hahner's finishing
    times in\\the 2016 women's Olympic
  marathon}}\author{David Cottrell\thanks{Postdoctoral Research
  Fellow, Program in Quantitative Social Science, Dartmouth College,
    6108 Silsby Hall, Hanover, NH
    03755 (\texttt{david.cottrell@dartmouth.edu}).} \and Michael C.\
  Herron\thanks{Visiting Scholar, Hertie School of Governance, Berlin,
    Germany, and Professor of Government, Dartmouth College, 6108
    Silsby Hall, Hanover, NH 03755
    (\texttt{michael.c.herron@dartmouth.edu}).}}

@@

The Kurschilgen accusation against the Hahner twins has two
components, that these two women ran slowly \emph{and} that they
finished simultaneously.  We suspect that Kurschilgen would not have
expressed ire at the Hahners had they finished in 1st and 2nd place in
Rio, hand-in-hand with wide grins, but of course we do not know this.
As such, our investigation of the charges that Kurschilgen offered
will distinguish between the idea of slow finish versus a simultaneous
finish.

Our research design is twofold.  First, we present visualizations that
describe various features of the Hahner twin's results, and an
important element in our visualizations is the difference between a
runner's Rio time and her prior personal best time in the marathon.
Overall, our visualizations suggest that the Hahner twins' pace in the
marathon was slow, but not excessively so, but that their simultaneous
finish was quite unusual given the twins' differences in abilities
(and similarly for the Kim twins).  We then turn to a regression-based
simulation of the marathon, which we develop based on relationships
(excluding the Hahner and Kim twins and Luik triplets) between known
personal best times and observed Rio finishing times.  Our simulations
show that the Hahner twins finished suspiciously close to each other
given the disparty between their personal best times.  Finally, we
return to Kurschilgen claims about the Hahners and offer our thoughts
about their validity.

@@

\begin{figure}[!ht]
 \caption{Differences in personal best times and finishing times}
 \centering
 \begin{subfigure}{.49\textwidth}
 \includegraphics[width=\textwidth, keepaspectratio]{diff_in_diff_scatter_plot.pdf}
  \label{fig:diffdiffscatter}
 \end{subfigure}
  \begin{subfigure}{.49\textwidth}
 \includegraphics[width=\textwidth, keepaspectratio]{diff_in_diff_scatter_plot_half.pdf}
  \label{fig:diffdiffscatterhalf}
 \end{subfigure}
\end{figure}

>>>>

\title{\Large{All in the family:\\German twin finishing times in\\the
    2016 women's Olympic marathon}}\author{David
  Cottrell\thanks{Postdoctoral Research Fellow, Program in
    Quantitative Social Science, Dartmouth College, 6108 Silsby Hall,
    Hanover, NH 03755 (\texttt{david.cottrell@dartmouth.edu}).} \and
  Michael C.\ Herron\thanks{Visiting Scholar, Hertie School of
    Governance, Berlin, Germany, and Professor of Government,
    Dartmouth College, 6108 Silsby Hall, Hanover, NH 03755
    (\texttt{michael.c.herron@dartmouth.edu}).}}

@@

The Kurschilgen accusation against the Hahner twins has two
components, that these two women ran slowly \emph{and} that they
finished simultaneously.  We suspect that Kurschilgen would not have
expressed ire at the Hahners had they finished in 1st and 2nd place in
Rio, hand-in-hand with wide grins, but of course we do not know this.
As such, our investigation of the charges that Kurschilgen offered
will distinguish between a slow finish versus a simultaneous finish.

Our research design is twofold.  First, we present visualizations that
describe various features of the Hahner twin's results, and an
important element in our visualizations is the difference between a
runner's Rio time and her prior personal best time in the marathon.
Overall, our visualizations suggest that the Hahner twins' pace in the
marathon was slow, albeit not excessively so, but that their
simultaneous finish was quite unusual given the twins' differences in
abilities (and similarly for the Kim twins).  We then turn to a
regression-based simulation of the marathon, which we develop based on
relationships across the Olympic marathoners between personal best
times and observed Rio finishing times.  Our simulations show that the
Hahner twins did not run appreciably slowly yet finished suspiciously
close to each other given the disparty between their personal best
times.  We return in our conclusion to Kurschilgen's claims about the
Hahners and offer our thoughts about their validity.

@@

\begin{figure}[!ht]
 \caption{Differences in personal best times and finishing times}
  \label{fig:diffdiff}
 \centering
 \begin{subfigure}{.49\textwidth}
 \includegraphics[width=\textwidth, keepaspectratio]{diff_in_diff_scatter_plot.pdf}
 \caption{}
  \label{fig:diffdiffscatter}
 \end{subfigure}
  \begin{subfigure}{.49\textwidth}
 \includegraphics[width=\textwidth, keepaspectratio]{diff_in_diff_scatter_plot_half.pdf}
 \caption{}
  \label{fig:diffdiffscatterhalf}
 \end{subfigure}
\end{figure}
